### 2016-03-22 paper.tex
Insert Kay's prose on cultural empathy and literacy
There are also some extra additions to the references file, for future use.

\section{Cultural Empathy and Monsters}

\textit{Kay will write something here that justifies the idea of using this kind of game to teach cultural empathy, using Monsters as a hook}

>>>>

\section{Cultural Empathy}

We have discussed how \totan{} uses cultural understanding, not only on a
small scale as a way to reward players, but also as a key takeaway of
the game. In order for the game to reward players for their cultural
understanding, we have to present cultures in a way that they can, to
some extent, be understood. In other words, our game needs to foster a
sense of \textit{cultural empathy}, defining ``empathy'' as 
the ``state of mind in which someone shares the feelings or outlook of
another, sometimes prompted by imaginative exercises 'stepping into
someone's shoes'''~\citep[p.242]{Honderich2005}
Therefore, cultural
empathy, loosely formed, is having empathy for others who are from
different cultures, which allows for better understanding of that
culture.

This goal of cultural empathy differs from a goal of \textit{cultural
literacy} which prepares individuals to participate in another culture
based on the information of the culture that they have been 
given~\citep[p.165]{Hirsch1983}. Being culturally literate is having the
ability to be able to participate in another culture that you are
``dropped into,'' similar to how being literate is having the ability to
understand or write a given work of text.  \totan{} focuses on a certain
level of literacy of the given culture. Players are rewarded for their
cultural understanding and their ability to ``perform'' in the given
culture because of the information they have. This is demonstrated in
the example above, understanding the cultural views of marriage and
sex-change have an important role in game play. However, cultural
empathy makes the main point the understanding, not the
performance. \totan{} relies on an understanding of cultural values as
opposed to just focusing on some of their values consequential
norms. Therefore, though \totan{} expects some sense of cultural
literacy, it focuses more on cultural empathy. When a player walks
away from the game they would not have gained the ability to
participate in either a Middle Eastern or South Asian culture;
however, they will have gained an understanding of that culture. 
%This
%is why our emphasis in creating the game has relied more on cultural
%empathy than cultural literacy. We focus more on a mindset of a
%culture, than about facts about the culture. 
In the context of the
game, cultural empathy is a means to the end of cultural
literacy. However, outside of the game, focusing on cultural literacy
within a semi-fictional world works as the means for cultivating
cultural empathy, particularly world culture empathy.
